---
title: "NHOP"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: flatly
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(flexdashboard)
library(DT)
library(dplyr)
library(tidyr)
library(readxl)
library(forcats)
library(DataExplorer)
library(eeptools)
library(patchwork)
library(leaflet)
library(tidytext)
library(googlesheets4)
gs4_deauth()
theme_set(theme_light())
#flatly
#united
```


```{r}
# df <- read_excel("sample-data/Database as of 26.01.21.xlsx", sheet = 1)
# df <- read_excel("sample-data/NEW/Data Nansana -Ganda(AutoRecovered).xlsx")
df <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1l8cQWfJAy1UdnLgOKHe7twpv6UrrIQHUkmIP2VY3_QU/edit?usp=sharing")

# df <- readxl::read_excel("/home/nice-bsa/Downloads/NHOP_agents_database_shoreline.xlsx")
processed_df <- df %>% 
  select( "_index",
          "group_ev6dr15/rec_date",
          "group_ev6dr15/r_name",
          "group_ev6dr15/surname",
          "Trained",
          "signed contract",
          "group_ev6dr15/Adress_details",
          "group_ev6dr15/location_district",
          "group_ev6dr15/location_subcounty",
          "group_ev6dr15/location",
          "group_ev6dr15/Village",
          "group_ev6dr15/dob",
          # "group_ev6dr15/year",
          "group_ev6dr15/assign_id",
          "group_ev6dr15/id",
          "group_ev6dr15/sex",
          "group_ev6dr15/Marital_status",
          "group_ev6dr15/tel",
          "group_ev6dr15/kin",
          "group_ev6dr15/kin_address",
          "group_ev6dr15/kin_tel",
          "group_ev6dr15/kin_id",
          "group_sc15r33/business",
          "group_sc15r33/type_business",
          "group_sc15r33/where",
          "group_sc15r33/premise",
          "group_sc15r33/period_opn",
          "group_sc15r33/num_staff",
          "group_sc15r33/customers",
          "group_sc15r33/freq_purchases",
          "group_sc15r33/suppliers",
          "group_sc15r33/exprn",
          "group_sc15r33/If_yes_tick_appropriately",
          "group_sc15r33/If_yes_tick_appropriately/1",
          "group_sc15r33/If_yes_tick_appropriately/2",
          "group_sc15r33/If_yes_tick_appropriately/3",
          "group_sc15r33/saving",
          "group_sc15r33/saving_scheme",
          "group_sc15r33/saving_scheme/saving_group",             
          # "group_sc15r33/saving_scheme/micro_finance_institution",
          "group_sc15r33/saving_scheme/sacco",                    
          "group_sc15r33/saving_scheme/bank",                     
          "group_sc15r33/loan",             
          "group_sc15r33/loan_src",
          "group_sc15r33/loan_src/saving_group",              
          "group_sc15r33/loan_src/sacco",                     
          # "group_sc15r33/loan_src/microfinance_institution ",  
          "group_sc15r33/loan_src/bank",                      
          "group_sc15r33/loan_src/friends_and_family",
          "group_sc15r33/loan_amt",
           "group_sc15r33/serv_loan",
          "group_sc15r33/ern/gross_profit",
          # "group_sc15r33/ern/net_profit",
          "group_sc15r33/need",
          "group_sc15r33/training",
          "group_sc15r33/products/nhop1",  # NHOP products you know
          "group_sc15r33/products/nhop2",                         
          "group_sc15r33/products/nhop3",                         
          "group_sc15r33/goals/goal1",    # Goal                   
          "group_sc15r33/goals/goal2",                            
          "group_sc15r33/goals/goal3",                            
          "group_sc15r33/motivation/mot1",  # Motivation           
          "group_sc15r33/motivation/mot2",                        
          "group_sc15r33/motivation/mot3",                        
          "group_sc15r33/activation" , # Activation                
          "group_sc15r33/why/reason1",   # Why                     
          "group_sc15r33/why/reason2",                            
          "group_sc15r33/why/reason3",                            
          "group_sc15r33/will_train",   # Are you willing to train 
          # "GPS",           # GPS                     
          "_GPS_latitude",        
          "_GPS_longitude",      
          # "_GPS_altitude",     
          # "_GPS_precision",  
        )%>% 
  rename("ID" = "_index", ## --------
         "date" = "group_ev6dr15/rec_date",
         "first_name" = "group_ev6dr15/r_name",
          "surname" = "group_ev6dr15/surname",
          "signed_contract" = `signed contract`,
          "address_details" = "group_ev6dr15/Adress_details", 
          "district" = "group_ev6dr15/location_district",
          "sub_county" =  "group_ev6dr15/location_subcounty",
          "location" = "group_ev6dr15/location",              
          "village" = "group_ev6dr15/Village",              
          "date_of_birth" = "group_ev6dr15/dob",               
          # "year" = "group_ev6dr15/year",         ## --------              
          "assign_ID" = "group_ev6dr15/assign_id",
          "identification" = "group_ev6dr15/id",
          "gender" = "group_ev6dr15/sex",
          "maritus_status" =  "group_ev6dr15/Marital_status", 
          "telephone" = "group_ev6dr15/tel",              
          "next_kin" = "group_ev6dr15/kin",                 
          "next_of_kin_address" = "group_ev6dr15/kin_address", 
          "next_of_kin_tel" = "group_ev6dr15/kin_tel",       
          "next_of_kin_ID" = "group_ev6dr15/kin_id", 
          "business" = "group_sc15r33/business",                  
          "type_of_business" = "group_sc15r33/type_business",       
          "business_location" = "group_sc15r33/where",             
          "status_of_premises" = "group_sc15r33/premise",             
          "how_long_in_biz" = "group_sc15r33/period_opn",              
          "staff_employed" = "group_sc15r33/num_staff",              
          "customers_served" = "group_sc15r33/customers",            
          "frequency_of_purchase" = "group_sc15r33/freq_purchases",   
          "suppliers" = "group_sc15r33/suppliers",        
          "do_you_have_biz_experience" = "group_sc15r33/exprn",  
          "for_how_long" = "group_sc15r33/If_yes_tick_appropriately", 
          "are_you_in_a_savings_group" = "group_sc15r33/saving",
          "type_of_saving_scheme" =  "group_sc15r33/saving_scheme",
          "ever_taken_a_loan" = "group_sc15r33/loan",
          "where_loan_was_taken_from" = "group_sc15r33/loan_src",
          "loan_amount" = "group_sc15r33/loan_amt",          
          "how_long" = "group_sc15r33/serv_loan",             
          "gross_profit" = "group_sc15r33/ern/gross_profit",  
          # "net_profit" = "group_sc15r33/ern/net_profit",
          "requests" = "group_sc15r33/need",
          "ever_gone_through_training" = "group_sc15r33/training",
          "activation" =  "group_sc15r33/activation",
          "are_you_willing_to_train" = "group_sc15r33/will_train",
          "latitude" = "_GPS_latitude",   
          "longitude" = "_GPS_longitude"  
         ) %>% 
  # REMVOE THESE COLUMNS
  select(-contains("saving_scheme")) %>% 
  select(-contains("loan_src")) %>% 
  select(-contains("if_yes_tick_appro")) %>%   

  # fix the 2 Yes in the dataset
  mutate(Trained = ifelse(Trained == "yes", "Yes", Trained)) %>% 
  mutate(signed_contract = ifelse(signed_contract == "yes", "Yes", signed_contract)) %>%
  as_tibble()
```

## Row

### Number of Females Registered

```{r}
registered_c_female <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  count(gender) %>% 
  filter(gender == 'female') %>% 
  pull(n)

valueBox(registered_c_female, icon = "fa-female", color = "success")
```

### Number of Males Registered

```{r}
registered_c_male <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  count(gender) %>% 
  filter(gender == 'male') %>% 
  pull(n)

valueBox(registered_c_male, icon = "fa-male", color = "info")
```

### Unknown Genders Registered

```{r}
registered_c_unknown <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  count(gender) %>% 
  filter(is.na(gender)) %>% 
  pull(n)

valueBox(0, icon = "fa-question", color = "primary")
```

### Total Number of Registered

```{r}
registered_c_total <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>%
  count(gender) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

valueBox(registered_c_total, icon = "fa-plus",color = "warning")
```

## Row

### Number of Females Trained

```{r}
trained_c_female <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(gender == 'female') %>% 
  count(Trained) %>% 
  filter(!is.na(Trained)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

valueBox(trained_c_female, icon = "fa-female", color = "success")
```

### Number of Males Trained

```{r}
trained_c_male <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(gender == 'male') %>% 
  count(Trained) %>% 
  filter(!is.na(Trained)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

valueBox(trained_c_male, icon = "fa-male", color = "info")
```

### Unknown Gender Trained

```{r}
trained_c_unknown<- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(is.na(gender)) %>% 
  count(Trained) %>% 
  filter(!is.na(Trained)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

valueBox(trained_c_unknown, icon = "fa-question", color = "primary")
```

### Total Number of People Trained

```{r}
trained_c_total <-processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  count(Trained) %>% 
  filter(!is.na(Trained)) %>%
  summarise(total = sum(n)) %>% 
  pull(total)

valueBox(trained_c_total, icon = "fa-plus",color = "warning")
```

## Row

### Number of Females: Signed Contracts

```{r}
signed_c_female <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(gender == 'female') %>%
  count(signed_contract) %>% 
  filter(!is.na(signed_contract)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

valueBox(signed_c_female, icon = "fa-female", color = "success")
```

### Number of Males: Signed Contracts

```{r}
signed_c_male <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(gender == 'male') %>%
  count(signed_contract) %>% 
  filter(!is.na(signed_contract)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

valueBox(signed_c_male, icon = "fa-male", color = "info")
```

### Unknown Gender: Signed Contracts

```{r}
signed_c_unknown <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(is.na(gender)) %>% 
  count(signed_contract) %>% 
  filter(!is.na(signed_contract)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

valueBox(signed_c_unknown, icon = "fa-question", color = "primary")
```

### Total Number of People: Signed Contracts

```{r}
total_signed_c <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  # filter(is.na(gender)) %>% 
  count(signed_contract) %>% 
  filter(!is.na(signed_contract)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

valueBox(total_signed_c, icon = "fa-plus",color = "warning")
```

## Row {data-height="100"}

<center><p class="h2">Graphs & Plots</p></center>

## Row {.tabset .tabset-fade}

### Map

```{r}
map_df <- processed_df %>% 
  select(longitude, latitude)

map_dff <- unique(map_df)
leaflet(data = map_dff) %>% 
  addTiles() %>%  
  addAwesomeMarkers(lng = ~longitude, 
                    lat = ~latitude) %>% 
  addPopups(32.6174124, 0.3135742, "NHOP") %>% 
  setView(lng = 32.6456595,
          lat = 0.320382,
          zoom = 9)
```

### Age Distribution

```{r fig.width=10, fig.height=5}
processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  mutate(age = age_calc(as.Date(date_of_birth), enddate = Sys.Date(), units = "years")) %>% 
  mutate(age = floor(age)) %>% 
  filter(age != 0) %>%
  filter(!is.na(gender)) %>% 
  ggplot(aes(age, fill = gender)) + 
  geom_histogram(binwidth = 1) + 
  geom_vline(aes(xintercept=18),
             color="black", linetype="dashed", size=.3)+
  geom_vline(aes(xintercept=35),  
             color="black", linetype="dashed", size=.3)+
  facet_grid(~gender) +
  ggtitle("Age Distribution for all Registered", 
          subtitle = "0 & NA Ages Filtered Out, Vertical Lines Show the Age Range(0-35)") +
  geom_text(stat='count', aes(label=..count..), vjust=-1) +
  ylim(0, 40) +
  ylab("# of People")

```

### Identification

```{r}
processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(!is.na(identification)) %>%
  # filter(!is.na(Trained)) %>% 
  mutate(Trained = ifelse(is.na(Trained), "Not Trained", Trained)) %>% 
  mutate(Trained = ifelse(Trained == "Yes", "Trained", Trained)) %>% 
  ggplot(aes(identification, fill = gender)) + geom_bar(position = "dodge") +
  facet_grid(.~Trained) +
  geom_text(stat='count', aes(label=..count..), vjust=-1) +
  ggtitle("What identification do Trained? UnTrained People have?")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ylim(0, 250)+
  ylab("# of People")
  # theme(legend.position="none")

```

### Business : Trained / NotTrained

```{r}
processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(!is.na(identification)) %>%
  # filter(!is.na(Trained)) %>% 
  mutate(Trained = ifelse(is.na(Trained), "Not Trained", Trained)) %>% 
  mutate(Trained = ifelse(Trained == "Yes", "Trained", Trained)) %>% 
  ggplot(aes(type_of_business, fill = Trained)) + 
  geom_bar(position = "dodge") +
  facet_grid(.~Trained) +
  geom_text(stat='count', aes(label=..count..), vjust=-1) +
  ggtitle("What Type of Business do Trained People Have?") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position="none") +
  ylim(0, 300) +
  ylab("# of People")
```

### Business : Trained & Signed
```{r}
processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(!is.na(identification)) %>%
  filter(!is.na(Trained)) %>% 
  mutate(Trained = ifelse(is.na(Trained), "No", Trained)) %>% 
  filter(signed_contract == "yes") %>% 
  ggplot(aes(type_of_business, fill = Trained)) + 
  geom_bar(position = "dodge") +
  # facet_grid(.~Trained) +
  geom_text(stat='count', aes(label=..count..), vjust=-1) +
  ggtitle("Type of Business Owned by those Trained and Signed") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position="none") +
  ylim(0, 50) +
  ylab("# of People")
```


### Frequency of purchase

```{r}
processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(!is.na(identification)) %>%
  # filter(!is.na(Trained)) %>% 
  mutate(Trained = ifelse(is.na(Trained), "No", Trained)) %>% 
  ggplot(aes(frequency_of_purchase)) + 
  geom_bar() +
  # facet_grid(.~gender) +
  ggtitle("Frequency of purchase") +
  geom_text(stat='count', aes(label=..count..), vjust=-1) +
  ylim(0, 250)
```

### Top 10 Most Popular Products

```{r}
processed_df %>% 
  pivot_longer(cols = contains("products"), 
               names_to = "products_col", 
               values_to = "products") %>%
  filter(!is.na(products)) %>%
  mutate(products = tolower(products)) %>% 
  mutate(products = ifelse(products == "basin", "basins", products)) %>% 
  mutate(products = ifelse(products == "nice basin\'s", "basins", products)) %>% 
  mutate(products = ifelse(products == "nice jerrycans", "jerrycans", products)) %>% 
  mutate(products = ifelse(products == "jerry cans", "jerrycans", products)) %>% 
  mutate(products = ifelse(products == "jerricans", "jerrycans", products)) %>% 
  mutate(products = ifelse(products == "jerry can", "jerrycans", products)) %>% 
  mutate(products = ifelse(products == "jerrican", "jerrycans", products)) %>% 
  mutate(products = ifelse(products == "nice toothbrush", "toothbrush", products)) %>% 
  mutate(products = ifelse(products == "bucket", "buckets", products)) %>% 
  mutate(products = ifelse(products == "nice baskets", "buckets", products)) %>% 
  mutate(products = ifelse(products == "plate", "plates", products)) %>% 
  mutate(products = ifelse(products == "nice watering can", "watering can", products)) %>% 
  mutate(products = ifelse(products == "watering can", "watering cans", products)) %>% 
  mutate(products = ifelse(products == "nice pens", "pens", products)) %>%
  mutate(products = ifelse(products == "sato", "satos", products)) %>%
  mutate(products = ifelse(products == "mug", "mugs", products)) %>%
  mutate(products = ifelse(products == "nice chairs", "chairs", products)) %>%
  mutate(products = ifelse(products == "tooth brush", "toothbrush", products)) %>%
  mutate(products = ifelse(products == "nice mugs", "mugs", products)) %>%
  count(products, sort = TRUE) %>% 
  head(11) %>% 
  mutate(products = fct_reorder(products, n)) %>%
  ggplot(aes(products, n)) +
  geom_col() +
  ggtitle("Top 10 Most Popular Products among all") +
  coord_flip() +
  labs(x="", y="Count") +
  ylim(0, 250)
```

### Common Words in Why/Reason

```{r}
processed_df %>%
pivot_longer(cols = contains("reason"),
             names_to = "reasons_col",
             values_to = "reason_for_participation") %>%
  filter(!is.na(reason_for_participation)) %>%
  unnest_tokens(word, reason_for_participation) %>%
  anti_join(stop_words, by="word") %>%
  # filter(!word %in% c("app", "safe", "boda", "safeboda")) %>%
  count(word, sort = TRUE) %>%
  head(20) %>%
  mutate(word = fct_reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  coord_flip() +
  ggtitle("Most Common Words in Why/Reason") +
  labs(x="", y="Count") + 
  ylim(0, 200)
```

```{r}
### Common Words in Goals
# processed_df %>%
# pivot_longer(cols = contains("goals"),
#              names_to = "goals_col",
#              values_to = "goal_for_participation") %>%
#   filter(!is.na(goal_for_participation)) %>%
#   unnest_tokens(word, goal_for_participation) %>%
#   anti_join(stop_words, by="word") %>%
#   # filter(!word %in% c("app", "safe", "boda", "safeboda")) %>%
#   count(word, sort = TRUE) %>%
#   head(20) %>%
#   mutate(word = fct_reorder(word, n)) %>%
#   ggplot(aes(word, n)) +
#   geom_col() +
#   coord_flip() +
#   labs(x="", y="Count")
```

```{r}
### Common Words in Motivation
# processed_df %>%
# pivot_longer(cols = contains("motivation"),
#              names_to = "motivation_col",
#              values_to = "motivation_for_participation") %>%
#   filter(!is.na(motivation_for_participation)) %>%
#   unnest_tokens(word, motivation_for_participation) %>%
#   anti_join(stop_words, by="word") %>%
#   # filter(!word %in% c("app", "safe", "boda", "safeboda")) %>%
#   count(word, sort = TRUE) %>%
#   head(20) %>%
#   mutate(word = fct_reorder(word, n)) %>%
#   ggplot(aes(word, n)) +
#   geom_col() +
#   coord_flip() +
#   labs(x="", y="Count")
```

### Missing Data

```{r fig.width=10, fig.height=10, fig.align='left'}
DataExplorer::plot_missing(processed_df)
```

## Row

### Dataset

```{r}
# DT::datatable(head(processed_df, 20))
```



