---
title: "NICE HOUSE OF PLASTICS"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: flatly
---

```{r setup, include=FALSE}
library(flexdashboard)
library(DT)
library(tidyverse)
library(readxl)
library(DataExplorer)
library(eeptools)
library(patchwork)
#flatly
#united
```

```{r}
df <- read_excel("sample-data/Database as at 12 Jan 2021.xlsx", na = c(NA, "", " "))

processed_df <- df %>% 
  select("_id",
         "group_ev6dr15/rec_date", 
         "group_ev6dr15/r_name",
         "group_ev6dr15/surname",
         "Trained",
         "Signed contract",
         "group_ev6dr15/Adress_details",
         "group_ev6dr15/location_district",
         "group_ev6dr15/location_subcounty",
         "group_ev6dr15/location",
         "group_ev6dr15/Village",
         "group_ev6dr15/dob",
         "group_ev6dr15/year",
         "group_ev6dr15/assign_id",
         "group_ev6dr15/id",
         "group_ev6dr15/sex",
         "group_ev6dr15/Marital_status",
         "group_ev6dr15/tel",
         "group_ev6dr15/kin",
         "group_ev6dr15/kin_address",
         "group_ev6dr15/kin_tel",
         "group_ev6dr15/kin_id",
         "group_sc15r33/business",
         "group_sc15r33/type_business",
         "group_sc15r33/where",
         "group_sc15r33/premise",
        "group_sc15r33/period_opn",
        "group_sc15r33/num_staff",
        "group_sc15r33/customers",
        "group_sc15r33/freq_purchases",
        "group_sc15r33/suppliers",
        "group_sc15r33/exprn",
        "group_sc15r33/If_yes_tick_appropriately",
        "group_sc15r33/If_yes_tick_appropriately/1",
        "group_sc15r33/If_yes_tick_appropriately/2",
        "group_sc15r33/If_yes_tick_appropriately/3",
        "group_sc15r33/saving",
        "group_sc15r33/saving_scheme",
        "group_sc15r33/saving_scheme/saving_group",             
        "group_sc15r33/saving_scheme/micro_finance_institution",
        "group_sc15r33/saving_scheme/sacco",                    
        "group_sc15r33/saving_scheme/bank",                     
        "group_sc15r33/loan",             
        "group_sc15r33/loan_src",
        "group_sc15r33/loan_src/saving_group",              
        "group_sc15r33/loan_src/sacco",                     
        "group_sc15r33/loan_src/microfinance_institution",  
        "group_sc15r33/loan_src/bank",                      
        "group_sc15r33/loan_src/friends_and_family",
        "group_sc15r33/loan_amt",
         "group_sc15r33/serv_loan",
        "group_sc15r33/ern/gross_profit",
        "group_sc15r33/ern/net_profit",
        "group_sc15r33/need",
        "group_sc15r33/training",
        "group_sc15r33/products/nhop1",  # NHOP products you know
        "group_sc15r33/products/nhop2",                         
        "group_sc15r33/products/nhop3",                         
        "group_sc15r33/goals/goal1",    # Goal                   
        "group_sc15r33/goals/goal2",                            
        "group_sc15r33/goals/goal3",                            
        "group_sc15r33/motivation/mot1",  # Motivation           
        "group_sc15r33/motivation/mot2",                        
        "group_sc15r33/motivation/mot3",                        
        "group_sc15r33/activation" , # activation                
        "group_sc15r33/why/reason1",   # Why                     
        "group_sc15r33/why/reason2",                            
        "group_sc15r33/why/reason3",                            
        "group_sc15r33/will_train",   # Are you willing to train 
        # "GPS",           # GPS                     
        "_GPS_latitude",        
        "_GPS_longitude",      
        # "_GPS_altitude",     
        # "_GPS_precision",  
        )%>% 
  rename("ID" = "_id",
         "date" = "group_ev6dr15/rec_date", 
         "first_name" = "group_ev6dr15/r_name",
          "surname" = "group_ev6dr15/surname",
          "address_details" = "group_ev6dr15/Adress_details", 
          "district" = "group_ev6dr15/location_district",
          "sub_county" =  "group_ev6dr15/location_subcounty",
          "location" = "group_ev6dr15/location",              
          "village" = "group_ev6dr15/Village",              
          "date_of_birth" = "group_ev6dr15/dob",               
          "year" = "group_ev6dr15/year",                       
          "assign_ID" = "group_ev6dr15/assign_id",
          "identification" = "group_ev6dr15/id",
          "gender" = "group_ev6dr15/sex",
          "maritus_status" =  "group_ev6dr15/Marital_status", 
          "telephone" = "group_ev6dr15/tel",              
          "next_kin" = "group_ev6dr15/kin",                 
          "next_of_kin_address" = "group_ev6dr15/kin_address", 
          "next_of_kin_tel" = "group_ev6dr15/kin_tel",       
          "next_of_kin_ID" = "group_ev6dr15/kin_id", 
          "business" = "group_sc15r33/business",                  
          "type_of_business" = "group_sc15r33/type_business",       
          "business_location" = "group_sc15r33/where",             
          "status_of_premises" = "group_sc15r33/premise",             
          "how_long_in_biz" = "group_sc15r33/period_opn",              
          "staff_employed" = "group_sc15r33/num_staff",              
          "customers_served" = "group_sc15r33/customers",            
          "frequency_of_purchase" = "group_sc15r33/freq_purchases",   
          "suppliers" = "group_sc15r33/suppliers",        
          "do_you_have_biz_experience" = "group_sc15r33/exprn",  
           "for_how_long" = "group_sc15r33/If_yes_tick_appropriately", 
          "are_you_in_a_savings_group" = "group_sc15r33/saving",
          "type_of_saving_scheme" =  "group_sc15r33/saving_scheme",
          "ever_taken_a_loan" = "group_sc15r33/loan",
          "where_loan_was_taken_from" = "group_sc15r33/loan_src",
          "loan_amount" = "group_sc15r33/loan_amt",          
          "how_long" = "group_sc15r33/serv_loan",             
          "gross_profit" = "group_sc15r33/ern/gross_profit",  
          "net_profit" = "group_sc15r33/ern/net_profit",
          "requests" = "group_sc15r33/need",
          "ever_gone_through_training" = "group_sc15r33/training",
          "activation" =  "group_sc15r33/activation",
          "are_you_willing_to_train" = "group_sc15r33/will_train",
          "latitude" = "_GPS_latitude",   
          "longitude" = "_GPS_longitude"  
         ) %>% 
  select(-contains("saving_scheme")) %>% 
  select(-contains("loan_src")) %>% 
  select(-contains("if_yes_tick_appro")) %>%   
  pivot_longer(cols = contains("products"), 
               names_to = "products_col", 
               values_to = "products") %>% 
  pivot_longer(cols = contains("goals"), 
               names_to = "goals_col", 
               values_to = "goals") %>% 
  pivot_longer(cols = contains("motivation"), 
               names_to = "motivation_col", 
               values_to = "motivations") %>% 
  pivot_longer(cols = contains("reason"), 
               names_to = "reasons_col", 
               values_to = "reason_for_participation") %>% 
  select(-c("products_col","goals_col","motivation_col", "reasons_col")) %>% 
  rename("signed_contract"=`Signed contract`) %>% 
  # fix the 2 Yes in the dataset
  mutate(Trained = ifelse(Trained == "yes", "Yes", Trained)) %>% 
  as_tibble()
```

Row {data-height=100}
-------------------------------------
<center><p class="h2">Summary Stats</p></center>

```{r}
#### FEMALE

registered_c_female <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  count(gender) %>% 
  filter(gender == 'female') %>% 
  pull(n)

registered_c_male <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  count(gender) %>% 
  filter(gender == 'male') %>% 
  pull(n)

registered_c_unknown <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  count(gender) %>% 
  filter(is.na(gender)) %>% 
  pull(n)

registered_c_total <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  count(gender) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)
```

Row
-----------------------------------------------------------------------
### Number of Females Registered

```{r}
valueBox(registered_c_female, icon = "fa-female", color = "success")
```

### Number of Males Registered

```{r}
valueBox(registered_c_male, icon = "fa-male", color = "info")
```

### Unknown Genders Registered
```{r}
valueBox(registered_c_unknown, icon = "fa-question", color = "primary")
```

### Total Number of Registered

```{r}
valueBox(registered_c_total, icon = "fa-plus",color = "warning")
```

```{r}
#### TRAINED VS UNTRAINED
trained_c_male <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(gender == 'male') %>% 
  count(Trained) %>% 
  filter(!is.na(Trained)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

trained_c_female <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(gender == 'female') %>% 
  count(Trained) %>% 
  filter(!is.na(Trained)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

trained_c_unknown<- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(is.na(gender)) %>% 
  count(Trained) %>% 
  filter(!is.na(Trained)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

trained_c_total <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  count(Trained) %>% 
  filter(!is.na(Trained)) %>%
  summarise(total = sum(n)) %>% 
  pull(total)

```
Row
-----------------------------------------------------------------------
### Number of Females Trained

```{r}
valueBox(trained_c_female, icon = "fa-female", color = "success")
```

### Number of Males Trained

```{r}
valueBox(trained_c_male, icon = "fa-male", color = "info")
```

### Uknown Gender Trained
```{r}
valueBox(trained_c_unknown, icon = "fa-question", color = "primary")
```

### Total Number of People Trained

```{r}
valueBox(trained_c_total, icon = "fa-plus",color = "warning")
```

```{r}
signed_c_female <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(gender == 'female') %>%
  count(signed_contract) %>% 
  filter(!is.na(signed_contract)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

signed_c_male <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(gender == 'male') %>%
  count(signed_contract) %>% 
  filter(!is.na(signed_contract)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

signed_c_unknown <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(is.na(gender)) %>% 
  count(signed_contract) %>% 
  filter(!is.na(signed_contract)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)

total_signed_c <- processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  # filter(is.na(gender)) %>% 
  count(signed_contract) %>% 
  filter(!is.na(signed_contract)) %>% 
  summarise(total = sum(n)) %>% 
  pull(total)
```

Row
-----------------------------------------------------------------------
### Number of Females: Signed Contracts

```{r}
valueBox(signed_c_female, icon = "fa-female", color = "success")
```

### Number of Males: Signed Contracts

```{r}
valueBox(signed_c_male, icon = "fa-male", color = "info")
```

### Uknown Gender: Signed Contracts
```{r}
valueBox(signed_c_unknown, icon = "fa-question", color = "primary")
```

### Total Number of People: Signed Contracts

```{r}
valueBox(total_signed_c, icon = "fa-plus",color = "warning")
```

Row {data-height=100}
-------------------------------------
<center><p class="h2">Graphs & Plots</p></center>

Row {.tabset .tabset-fade}
-------------------------------------
   
### Age
    
```{r fig.width=10, fig.height=5}
processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  mutate(age = age_calc(as.Date(date_of_birth), enddate = Sys.Date(), units = "years")) %>% 
  mutate(age = floor(age)) %>% 
  filter(age != 0) %>%
  filter(!is.na(gender)) %>% 
  ggplot(aes(age, fill = gender)) + 
  geom_histogram(binwidth = 1) + 
  geom_vline(aes(xintercept=18),
             color="black", linetype="dashed", size=.3)+
  geom_vline(aes(xintercept=35),  
             color="black", linetype="dashed", size=.3)+
  facet_grid(~gender) +
  ggtitle("Age Distribution for all Registered", 
          subtitle = "0 & NA Ages Filtered Out, Vertical Lines Show the Age Range(0-35)") +
  geom_text(stat='count', aes(label=..count..), vjust=-1)

```

### identification
    
```{r}
processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(!is.na(identification)) %>%
  # filter(!is.na(Trained)) %>% 
  mutate(Trained = ifelse(is.na(Trained), "No", Trained)) %>% 
  ggplot(aes(identification, fill = gender)) + geom_bar(position = "dodge") +
  facet_grid(.~Trained) +
  geom_text(stat='count', aes(label=..count..), vjust=-1) +
  ggtitle("What identification do Trained People have?")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  # theme(legend.position="none")

```

### Business Type
    
```{r}
processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(!is.na(identification)) %>%
  # filter(!is.na(Trained)) %>% 
  mutate(Trained = ifelse(is.na(Trained), "No", Trained)) %>% 
  ggplot(aes(type_of_business, fill = Trained)) + 
  geom_bar(position = "dodge") +
  facet_grid(.~Trained) +
  geom_text(stat='count', aes(label=..count..), vjust=-1) +
  ggtitle("What Type of Business do Trained People Have?") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

### Frequency of purchase

```{r}
processed_df %>% 
  add_count(ID) %>% 
  filter(!duplicated(ID)) %>% 
  filter(!is.na(identification)) %>%
  # filter(!is.na(Trained)) %>% 
  mutate(Trained = ifelse(is.na(Trained), "No", Trained)) %>% 
  ggplot(aes(frequency_of_purchase)) + 
  geom_bar() +
  # facet_grid(.~gender) +
  geom_text(stat='count', aes(label=..count..), vjust=-1)
```  

### Requests

```{r}

```  

### Missing Data

```{r fig.width=10, fig.height=10, fig.align='left'}
DataExplorer::plot_missing(processed_df)
```  

Row 
-------------------------------------
    
### Dataset
    
```{r}
DT::datatable(head(processed_df, 20))
```

